---
title: "Homework 11" 
author: "Carlos F Revilla"
fontsize: 12pt
geometry: margin=1in
urlcolor: black
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, highlight=FALSE, warning=FALSE)
# Set the random seed
set.seed(06222001)
```

## Problem 1   
```{r}
# Define the probability of success and the number of trials
p <- 0.5
n <- 104

# Define the number of repetitions for the Monte Carlo simulation
reps <- 10000

# Perform the Monte Carlo simulation for each test
left_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = FALSE)$p.value)
left_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = TRUE)$p.value)
right_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", correct = FALSE)$p.value)
right_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", correct = TRUE)$p.value)
two_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", correct = FALSE)$p.value)
two_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", correct = TRUE)$p.value)

# Print the empirical Type I error for each test
print(paste("Left-tailed without continuity correction:", mean(left_tailed_no_cc < 0.05)))
print(paste("Left-tailed with continuity correction:", mean(left_tailed_cc < 0.05)))
print(paste("Right-tailed without continuity correction:", mean(right_tailed_no_cc < 0.05)))
print(paste("Right-tailed with continuity correction:", mean(right_tailed_cc < 0.05)))
print(paste("Two-tailed without continuity correction:", mean(two_tailed_no_cc < 0.05)))
print(paste("Two-tailed with continuity correction:", mean(two_tailed_cc < 0.05)))
```

## Problem 2   
```{r}
# Define the probability of success and the number of trials
p <- 0.5
n <- 104

# Define the alternative value and the number of repetitions for the Monte Carlo simulation
alternative <- 0.55
reps <- 10000

# Perform the Monte Carlo simulation
left_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = FALSE, p = alternative)$p.value)
left_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = TRUE, p = alternative)$power)
right_tailed_no_cc <- replicate(reps, binom.test(x = 45, n = n, p = p, alternative = "greater", correct = FALSE)$p.value)
right_tailed_cc <- replicate(reps, binom.test(x = 45, n = n, p = p, alternative = "greater", correct = TRUE)$p.value)
two_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", p.value = 0.45, correct = FALSE)$p.value)
two_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", p.value = 0.45, correct = TRUE)$p.value)
# Print the empirical power for the test
print(paste("Left-tailed without continuity correction:", mean(left_tailed_no_cc < 0.05)))
print(paste("Left-tailed with continuity correction:", mean(left_tailed_cc < 0.05)))
print(paste("Right-tailed (more than 45%) without continuity correction:", mean(right_tailed_no_cc < 0.05)))
print(paste("Right-tailed (more than 45%) with continuity correction:", mean(right_tailed_cc < 0.05)))
print(paste("Two-tailed (is not 45%) without continuity correction:", mean(two_tailed_no_cc < 0.05)))
print(paste("Two-tailed (is not 45%) with continuity correction:", mean(two_tailed_cc < 0.05)))
```
## Problem 3   
```{r}
# Define the probability of success and the number of trials
p <- 0.5
n <- 104

# Define the number of repetitions for the Monte Carlo simulation
reps <- 10000

# Perform the Monte Carlo simulation for each test
left_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = FALSE)$p.value)
left_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = TRUE)$p.value)
right_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", correct = FALSE)$p.value)
right_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", correct = TRUE)$p.value)
two_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", correct = FALSE)$p.value)
two_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", correct = TRUE)$p.value)

results <- data.frame(
  Test = c(
    "Left-tailed without continuity correction",
    "Left-tailed with continuity correction",
    "Right-tailed without continuity correction",
    "Right-tailed with continuity correction",
    "Two-tailed without continuity correction",
    "Two-tailed with continuity correction"
  ),
  Empirical_Type_I_Error = c(
    mean(left_tailed_no_cc < 0.05),
    mean(left_tailed_cc < 0.05),
    mean(right_tailed_no_cc < 0.05),
    mean(right_tailed_cc < 0.05),
    mean(two_tailed_no_cc < 0.05),
    mean(two_tailed_cc < 0.05)
  )
)

# Print the results in a tabular-like structure
knitr::kable(results)
```

## Problem 4   
```{r}
# Define the probability of success and the number of trials
p <- 0.5
n <- 104

# Define the number of repetitions for the Monte Carlo simulation
reps <- 10000

# Perform the Monte Carlo simulation for each test
two_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", p.value = 0.45, correct = FALSE)$p.value)
two_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", p.value = 0.45, correct = TRUE)$p.value)

# Create a data frame to store the results
results <- data.frame(
  Test = c("Two-tailed (is not 45%) without continuity correction", "Two-tailed (is not 45%) with continuity correction"),
  Empirical_Power = c(mean(two_tailed_no_cc < 0.05), mean(two_tailed_cc < 0.05))
)

# Print the results
results
```

## Problem 5   
```{r}
# Define the probability of success and the number of trials
p <- 0.1
n <- 104

# Define the number of repetitions for the Monte Carlo simulation
reps <- 10000

# Perform the Monte Carlo simulation for each test
left_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = FALSE)$p.value)
left_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = TRUE)$p.value)
right_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", correct = FALSE)$p.value)
right_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", correct = TRUE)$p.value)
two_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", correct = FALSE)$p.value)
two_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", correct = TRUE)$p.value)

# Print the empirical Type I error for each test
print(paste("Left-tailed without continuity correction:", mean(left_tailed_no_cc < 0.05)))
print(paste("Left-tailed with continuity correction:", mean(left_tailed_cc < 0.05)))
print(paste("Right-tailed without continuity correction:", mean(right_tailed_no_cc < 0.05)))
print(paste("Right-tailed with continuity correction:", mean(right_tailed_cc < 0.05)))
print(paste("Two-tailed without continuity correction:", mean(two_tailed_no_cc < 0.05)))
print(paste("Two-tailed with continuity correction:", mean(two_tailed_cc < 0.05)))
```

## Problem 6   
```{r}
# Define the probability of success and the number of trials
p <- 0.1
n <- 104

# Define the number of repetitions for the Monte Carlo simulation
reps <- 10000

# Perform the Monte Carlo simulation for each test
left_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", p.value = 0.15, correct = FALSE)$p.value)
left_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", p.value = 0.15, correct = TRUE)$p.value)
right_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", p.value = 0.05, correct = FALSE)$p.value)
right_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", p.value = 0.05, correct = TRUE)$p.value)
two_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", p.value = 0.05, correct = FALSE)$p.value)
two_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", p.value = 0.05, correct = TRUE)$p.value)

# Print the empirical power for each test
print(paste("Left-tailed (less than 15%) without continuity correction:", mean(left_tailed_no_cc < 0.05)))
print(paste("Left-tailed (less than 15%) with continuity correction:", mean(left_tailed_cc < 0.05)))
print(paste("Right-tailed (more than 5%) without continuity correction:", mean(right_tailed_no_cc < 0.05)))
print(paste("Right-tailed (more than 5%) with continuity correction:", mean(right_tailed_cc < 0.05)))
print(paste("Two-tailed (is not 5%) without continuity correction:", mean(two_tailed_no_cc < 0.05)))
print(paste("Two-tailed (is not 5%) with continuity correction:", mean(two_tailed_cc < 0.05)))

```

## Problem 7   
```{r}

# Define the probability of success and the number of trials
p <- 0.1
n <- 104

# Define the number of repetitions for the Monte Carlo simulation
reps <- 10000

# Perform the Monte Carlo simulation for each test
left_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = FALSE)$p.value)
left_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", correct = TRUE)$p.value)
right_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", correct = FALSE)$p.value)
right_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", correct = TRUE)$p.value)
two_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", correct = FALSE)$p.value)
two_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", correct = TRUE)$p.value)

results <- data.frame(
  Test = c(
    "Left-tailed without continuity correction",
    "Left-tailed with continuity correction",
    "Right-tailed without continuity correction",
    "Right-tailed with continuity correction",
    "Two-tailed without continuity correction",
    "Two-tailed with continuity correction"
  ),
  Empirical_Type_I_Error = c(
    mean(left_tailed_no_cc < 0.05),
    mean(left_tailed_cc < 0.05),
    mean(right_tailed_no_cc < 0.05),
    mean(right_tailed_cc < 0.05),
    mean(two_tailed_no_cc < 0.05),
    mean(two_tailed_cc < 0.05)
  )
)

print(results)
```

## Problem 8   
```{r}
# Define the probability of success and the number of trials
p <- 0.1
n <- 104

# Define the number of repetitions for the Monte Carlo simulation
reps <- 10000

# Perform the Monte Carlo simulation for each test
left_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", p.value = 0.15, correct = FALSE)$p.value)
left_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "less", p.value = 0.15, correct = TRUE)$p.value)
right_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", p.value = 0.05, correct = FALSE)$p.value)
right_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "greater", p.value = 0.05, correct = TRUE)$p.value)
two_tailed_no_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", p.value = 0.05, correct = FALSE)$p.value)
two_tailed_cc <- replicate(reps, binom.test(x = 0, n = n, p = p, alternative = "two.sided", p.value = 0.05, correct = TRUE)$p.value)

results <- data.frame(
  Test = c(
    "Left-tailed without continuity correction",
    "Left-tailed with continuity correction",
    "Right-tailed without continuity correction",
    "Right-tailed with continuity correction",
    "Two-tailed without continuity correction",
    "Two-tailed with continuity correction"
  ),
  Empirical_Type_I_Error = c(
    mean(left_tailed_no_cc < 0.05),
    mean(left_tailed_cc < 0.05),
    mean(right_tailed_no_cc < 0.05),
    mean(right_tailed_cc < 0.05),
    mean(two_tailed_no_cc < 0.05),
    mean(two_tailed_cc < 0.05)
  )
)

print(results)
```

## Problem 9   
When the sample size is large enough that the approximate normality assumption holds, the continuity correction to the one-sample z-test for proportions has a negligible effect on the Type I error and power of the test. This is because the continuity correction is a small adjustment to the test statistic that is used to account for the fact that the binomial distribution is discrete, rather than continuous. When the sample size is large, the binomial distribution approximates the normal distribution closely, so the continuity correction has little impact on the test. Therefore, in this situation, it is generally recommended to use the continuity correction to ensure that the Type I error of the test is correctly controlled. However, the choice of whether to use the continuity correction or not will not have a significant impact on the overall conclusions of the test.



